Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-29 Papers/ms.tex
Fixed awkward sentence

The model assumptions used in this paper are fairly simple. In future work we
intend to generalise the smooth lens model beyond the overly simplistic
SIE+$\gamma$ model, and to generalize the model to multi-band data. Applications
to other systems are also forthcoming, as well as variants on the model using
different conditional priors for the substructure properties given the
hyperparameters.

>>>>

The model assumptions used in this paper are fairly simple. In future work we
intend to generalize the model to multi-band data, and extend the
smooth lens model beyond the overly simplistic
SIE+$\gamma$ assumption. Applications
to other systems are also forthcoming, as well as variants on the model using
different conditional priors for the substructure properties given the
hyperparameters.
